\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-07 paper.qmd
Added script to generate C-shaped uniform and dense clusters, generate tSNE for both

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
```

@@

>>>>

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
source("scripts/five_gau_clusters/5_gen_model_with_tsne.R")
```

@@

```{r}
gen_proj_five_clust()[[1]] + gen_proj_five_clust()[[2]] + plot_layout(nrow = 2)
```

### 2025-01-07 paper.tex
Added script to generate C-shaped uniform and dense clusters, generate tSNE for both

\includegraphics[width=0.3\textwidth,height=\textheight]{paper_files/figure-pdf/fig-p-d-error-in-2d-two-curvy-1.pdf}

@@

@@

>>>>

\includegraphics[width=0.6\textwidth,height=\textheight]{paper_files/figure-pdf/fig-p-d-error-in-2d-two-curvy-1.pdf}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-51-1.pdf}
\end{center}

@@

To illustrate how the methods organise difference number of points
within the structure in the NLDR layout, simulated \(7\text{-}D\) data
having C-shaped structure is used.
